---
title: "R Notebook"
output: html_notebook

---
# Montant de snistres incendies
```{r}
donnee=read.table("http://math.univ-lyon1.fr/~fougeres/incendies-dk.txt")
```

##Hill.SSC
```{r}
# Computes the Hill estimates of gamma (Section 4.2) 
# for a numeric vector of observations (data) and as a
# function of k
#
# If plot=TRUE then the estimates are plotted as a
# function of k
#
# If add=TRUE then the estimates are added to an existing
# plot

"Hill" <- function(data, plot=FALSE, add=FALSE, ...) {
	
	X <- sort(data)
	n <- length(X)
	Hill <- numeric(n)
	K <- 1:(n-1)

### Hill estimates
	
for (k in 1:(n-1)) {
	Hill[k] <- (1/k)*sum(log(X[n:(n-k+1)])) - log(X[n-k])
	print(k)
}
	
### plots if TRUE

if (plot || add){
	if ( !add ) {   	### plot estimates
		plot(K, Hill[K], type="l", ylab="gamma", xlab="k", main="Estimates of extreme value index", ...)
	}
	else { 			### adds estimates to existing plot
		lines(K, Hill[K], ...)
	}
}

### output list with values of k and
### corresponding Hill estimates

list(k=K, gamma=Hill[K])

}
```

##WeissmanQ.SSC
```{r}
# Computes estimates of extreme quantile Q(1-p) 
# (Section 4.6.1) for a numeric vector of observations 
# (data) and as a function of k
#
# Estimates are based on prior estimates gamma for the
# extreme value index (Hill)
#
# If plot=TRUE then the estimates are plotted as a
# function of k
#
# If add=TRUE then the estimates are added to an existing
# plot


"Weissman.q" <- function(data, gamma, p, plot=FALSE, add=FALSE, ...) {
	
	X <- sort(data)
	n <- length(X)
	Weisman.q <- numeric(n)
	K <- 1:(n-1)

### Weisman estimator for quantiles
	
	Weisman.q[K] <- X[n-K]*((K+1)/((n+1)*p))^(gamma[K])
	
### plots if TRUE
k2=5:(n-10)
if (plot || add){
	if ( !add ) {   	### plot estimates
		plot(k2, Weisman.q[k2], type="l", ylab="Q(1-p)", xlab="k", main="Estimates of extreme quantile", ...)
	}
	else { 			### adds estimates to existing plot
		lines(K, Weisman.q[K], ...)
	}
}

### output list with values of k, corresponding quantile estimates 
### and the considered small tail probability p

list(k=K, Q=Weisman.q[K], p=p)

}
```

##WeissmanP.SSC
```{r}
# Computes estimates of small exceedance probability 1-F(q) 
# (Section 4.6.1) for a numeric vector of observations 
# (data) and as a function of k
#
# Estimates are based on prior estimates gamma for the
# extreme value index (Hill)
#
# If plot=TRUE then the estimates are plotted as a
# function of k
#
# If add=TRUE then the estimates are added to an existing
# plot

"Weissman.p" <- function(data, gamma, q, plot=FALSE, add=FALSE, ...) {
	
	X <- sort(data)
	n <- length(X)
	Weisman.p <- numeric(n)
	K <- 1:(n-1)

### Weisman estimator for probabilities
	
	Weisman.p[K] <- ((K+1)/(n+1))*(q/X[n-K])^(-1/gamma[K])
	
### plots if TRUE

if (plot || add){
	if ( !add ) {   	### plot estimates
		plot(K, Weisman.p[K], type="l", ylab="1-F(x)", xlab="k", main="Estimates of small exceedance probability", ...)
	}
	else { 			### adds estimates to existing plot
		lines(K, Weisman.p[K], ...)
	}
}

### output list with values of k, corresponding return period estimates 
### and the considered large quantile q

list(k=K, P=Weisman.p[K], q=q)

}
```

###graphe des montants de sinistres en fonction du temps:
```{r}
plot(1:2492,donnee$V1)
```

### Pareto quantile plot de l'échantillon entier
```{r}
install.packages("ReIns")
```
```{r}
library(ReIns)
```
```{r}
ParetoQQ(donnee$V1)
```

### Pareto quantile plot de l'échantillon des montants supérieurs à 1million
```{r}
V2=donnee$V1[which(donnee$V1>1)]
ParetoQQ(V2)
```

### Ajuster un modèle de Pareto généralisé
```{r}
install.packages("evd")
```

```{r}
library(evd)
```
#### via mrlplot : seuil à partir duquel on observe une relative linéarité
```{r}
mrlplot(donnee$V1)
```
Pour voir ce qui se passe entre 0 et 10
```{r}
mrlplot(donnee$V1, tlim=c(0,10))
```


#### via tcplot
```{r}
tcplot(donnee$V1,tlim=c(0,10))
```

Pour avoir le nombre d'observations supérieures à 2
```{r}
fitgpd=fpot(donnee$V1,2)
fitgpd$nhigh
fitgpd$estimate
```
scale=tau_chapeau, shape=gamma_shapeau
### Hill plot
```{r}
hill_plot=Hill(donnee$V1, plot=TRUE)
```

On a une certaine stabilité vers 400-450 sur le hill plot. Pour avoir la valeur de gamma en ce point on fait comme suit:
```{r}
hill_plot$gamma[450]
```
gamma_chapeau est à peu près égal à 0.7.
Avec fpot on trouvait 0.66. Cette estimation est inférieure à celle obtenue ave le hill plot.

### 3 estimations de la probabilité que le montant d'un sinistre incendie dépasse 55 millions de couronnes

#### 1ere estimation 
```{r}
V3=donnee$V1[which(donnee$V1>55)]
V3
prob1=length(V3)/length(donnee$V1)
prob1
```

#### 2eme estimation
```{r}
Weissman.p(donnee$V1,hill_plot$gamma,55,plot=TRUE)
```


### 3 estimations du quantile d'ordre 0.999
```{r}
Weissman.q(donnee$V1,hill_plot$gamma,0.999,plot=TRUE)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
